\documentclass[journal,twoside,web]{ieeecolor}
\usepackage{tmi}
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}

% Remove later
\usepackage{color,soul}
\newcommand{\TG}[1]{\color{blue}\textsc{From Tristan: }#1\color{black}}
\newcommand{\MD}[1]{\color{magenta}\textsc{From Mathieu: }#1\color{black}}
\newcommand{\HL}[1]{\hl{#1}}
% End of remove

\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\markboth{\journalname, VOL. XX, NO. XX, XXXX 2020}
{Author \MakeLowercase{\textit{et al.}}: Preparation of Papers for IEEE TRANSACTIONS ON MEDICAL IMAGING}
\begin{document}
\title{TODO: Title of the paper}
\author{Dugr\'e Mathieu, Chatelain Yohan, and Glatard Tristan
\thanks{This paragraph of the first footnote will contain the date on which
you submitted your paper for review. It will also contain support information,
including sponsor and financial support acknowledgment. For example, 
``This work was supported in part by the U.S. Department of Commerce under Grant BS123456.'' }
\thanks{The next few paragraphs should contain the authors' current affiliations,
including current address and e-mail. For example, F. A. Author is with the
National Institute of Standards and Technology, Boulder, CO 80305 USA (e-mail:author@boulder.nist.gov). }
\thanks{S. B. Author, Jr., was with Rice University, Houston, TX 77005 USA.
He is now with the Department of Physics, Colorado State University,
Fort Collins, CO 80523 USA (e-mail: author@lamar.colostate.edu).}
\thanks{T. C. Author is with the Electrical Engineering Department,
University of Colorado, Boulder, CO 80309 USA, on leave from the National
Research Institute for Metals, Tsukuba, Japan (e-mail: author@nrim.go.jp).}}
% TODO: Replace with our affiliations

\maketitle

\begin{abstract}
These instructions provide guidelines for preparing papers for IEEE Transactions,
but this version is specifically written to describe submission to IEEE TMI.
Use this document as a template if you are using \LaTeX.
Otherwise, use this document as an instruction set.
The electronic file of your paper will be formatted further at IEEE.
Paper titles should be written in uppercase and lowercase letters, not all uppercase.
Avoid writing long formulas with subscripts in the title;
short formulas that identify the elements are fine (e.g., "Nd--Fe--B").
Keep the title short and do not write ``(Invited)'' in the title.
Full names of authors are preferred in the author field, but are not required.
Put a space between authors' initials. Only authors may appear in the author line
of a manuscript. Authors are defined as individuals who have made an identifiable
intellectual contribution to a manuscript to the extent that the individual can defend its contents.
Define all symbols used in the abstract. Do not cite references in the abstract.
Keep the abstract to 250 words or less.
\end{abstract}

\begin{IEEEkeywords}
Enter about five key words or phrases in alphabetical order, separated by commas.
\end{IEEEkeywords}

\section{Introduction}
\label{sec:introduction}
% - Dugr\'e et al. 2025

% Context & Problem

% Importance

% Challenges

% Approach

% Contribution

% Outline


\section{Related Work}
\label{sec:related}
\subsection{Deep learning quantization techniques}


\subsection{Performance bottlenecks in ANTs registration}
% - Dugr\'e et al. 2025
% Interpolation and memory bounds. Can both benefit from quantization.


\subsection{Numerical stability of ANTs registration}
% Niusha's work on numerical stability of ANTs registration (Linear only)



\section{Method}
\label{sec:method}
\subsection{ANTs registration SyN}

\subsection{Theoretical analysis of minimum precision}
% - Hayford et al. 2024

\subsection{Evaluation of arbitrary data formats using VPREC}

\subsection{Dataset}

\subsection{Infrastructure}


\section{Experiments}
\label{sec:experiments}


\section{Results}
\label{sec:results}
\subsection{Estimating theoretical bounds on ANTs convergence}


\subsection{Data format space search}


\subsection{Performance evaluation of ANTs using single precision}


\section{Discussion}
\label{sec:discussion}
% Catastrophic failure with low precision initialization

% Assumptions on loss function convexity

% 




\section{Conclusion}
\label{sec:conclusion}


\appendices

\section*{Appendix and the Use of Supplemental Files}
Appendices, if needed, appear before the acknowledgment. If an appendix is not
critical to the main message of the manuscript and is included only for thoroughness
or for reader reference, then consider submitting appendices as supplemental materials.
Supplementary files are available to readers through IEEE \emph{Xplore\textregistered}
at no additional cost to the authors but they do not appear in print versions.
Supplementary files must be uploaded in ScholarOne as supporting documents, but for
accepted papers they should be uploaded as Multimedia documents. Refer readers
to the supplementary files where appropriate within the manuscript text using footnotes.
\footnote{Supplementary materials are available in the supporting documents/multimedia tab.
Further instructions on footnote usage are in the Footnotes section on the next page.}

\section*{Acknowledgment}
The preferred spelling of the word ``acknowledgment'' in American English is 
without an ``e'' after the ``g.'' Use the singular heading even if you have 
many acknowledgments. Avoid expressions such as ``One of us (S.B.A.) would 
like to thank $\ldots$ .'' Instead, write ``F. A. Author thanks $\ldots$ .'' In most 
cases, sponsor and financial support acknowledgments are placed in the 
unnumbered footnote on the first page, not here.

\bibliography{paper}
\end{document}
